Manuscript_Github_Pchabaudi_boilerplate

### 2022-08-03 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_TPMheatmaps.Rmd
Make labels for qusage comparison of chabaudi 24h

                    ht <- Heatmap(
                      log2(
                        1+ht.df
                      ),
                      cluster_rows = FALSE,
                      cluster_columns = FALSE,
                      show_row_names = FALSE,
                      name = 'log(TPM+1)', 
                      col = colorRamp2(c(0,
                                         maxcol/4,
                                         maxcol/2,
                                         3*maxcol/4,
                                         maxcol),
                                       viridis(5)),
                      na_col = 'white', 
                      border = TRUE,
                      border_gp = gpar(lwd = 0.1),
                      column_names_gp = gpar(fontsize = 10),
                      row_dend_width = unit(3, "cm"),
                      width = unit(4.5, 'cm'),
                      height = unit(7,'cm'),
                      column_title = paste(transmission),
                      row_title_rot = 0,
                      row_title_gp = gpar(fontsize = 10),
                      row_split = forcats::fct_shift(
                        relevel(
                          as.factor(combined_data_pir_ht$subfam),
                          ref = 'ref')
                      ),
                      heatmap_legend_param = list(
                        labels_gp = gpar(fontsize = 10),
                        title_gp = gpar(fontsize = 10,
                                        fontface = 'bold'),
                        at = c(0,
                               maxcol/4,
                               maxcol/2,
                               3*maxcol/4,
                               maxcol)
                      )
                    )
                    return(ht)
                  })

>>>>

                    ht <- Heatmap(
                      log2(
                        1+ht.df
                      ),
                      cluster_rows = FALSE,
                      cluster_columns = FALSE,
                      show_row_names = FALSE,
                      name = 'log(TPM+1)', 
                      col = colorRamp2(c(0,
                                         maxcol/4,
                                         maxcol/2,
                                         3*maxcol/4,
                                         maxcol),
                                       viridis(5)),
                      na_col = 'white', 
                      border = TRUE,
                      border_gp = gpar(lwd = 0.1),
                      column_names_gp = gpar(fontsize = 10),
                      row_dend_width = unit(3, "cm"),
                      width = unit(4.5, 'cm'),
                      height = unit(12,'cm'),
                      column_title = paste(transmission),
                      row_title_rot = 0,
                      row_title_gp = gpar(fontsize = 10),
                      row_split = forcats::fct_shift(
                        relevel(
                          as.factor(combined_data_pir_ht$subfam),
                          ref = 'ref')
                      ),
                      heatmap_legend_param = list(
                        labels_gp = gpar(fontsize = 10),
                        title_gp = gpar(fontsize = 10,
                                        fontface = 'bold'),
                        at = c(0,
                               maxcol/4,
                               maxcol/2,
                               3*maxcol/4,
                               maxcol)
                      )
                    )
                    return(ht)
                  })
